%%% Modified from a template taken from http://www.howtotex.com/
\documentclass[letterpaper,10pt]{article}

\usepackage{amsmath,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{array}
\usepackage{url}
\usepackage{hyperref}
\usepackage[letterpaper,margin=1in]{geometry}

% Font
\usepackage[T1]{fontenc}
\usepackage{quattrocento}\linespread{1}

% Sectioning
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{2pt plus 0pt minus 2pt}{0pt plus 2pt minus 2pt}
\usepackage{sectsty}                                                    % Custom sectioning (see below)
\sectionfont{\sectionrule{0pt}{0pt}{-5pt}{3pt}}

% Page style
\frenchspacing
\pagestyle{empty}

% Macros for sensitive information
\input{blank_personal_details}
%\input{real_personal_details}

% Page setup macros
\definecolor{light-gray}{gray}{0.7}

\newcommand{\sepspace}{\vspace*{0.3em}}

\newcommand{\MyName}[1]{
                \Huge \usefont{OT1}{phv}{b}{n}  #1 \hfill
                \par \normalsize \normalfont \sepspace}

\newcommand{\MySlogan}[1]{
                \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1} % Slogan (optional)
                \par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\vspace{-1em} \section*{\uppercase{#1}}}
\newcommand{\MainHeading}[1]{\noindent\textbf{#1}}
\newcommand{\SubHeading}[1]{\noindent\textit{#1}}
\newcommand{\DateBox}[1]{\colorbox{light-gray}{\parbox{8em}{\hfill\color{White}#1}}}
\newcommand{\Details}[1]{\hangindent=2em\hangafter=0\small#1\normalsize\par}

\newcommand{\WorkEntry}[4]{% Arguments are 1: Job name, 2: Dates, 3: Company, 4: Description
                \MainHeading{#1} \hfill \DateBox{#2} \par
                \SubHeading{#3} \par
                \noindent \hangindent=2em \hangafter=0 \Details{#4} }

\newcommand{\EducationEntry}[3]{% Arguments are 1: Degree, 2: Dates, 3: Description (Institution as a MainHeading beforehand)
                \SubHeading{#1} \hfill \DateBox{#2} \par
                \Details{#3} }


\begin{document}



% Name
\MyName{Pete Bunch}
%\MySlogan{Curriculum Vitae}
\vspace{0.5em}



% Personal details
%\NewPart{Personal details}
\noindent
\begin{tabular}{m{1.5cm} m{8.5cm} m{1.5cm} m{3cm}}
 \textit{Address:}    & \myaddress & 
 \textit{Phone:}      & \myphonenumber \\
 \textit{Email:}      & \href{mailto:\myemail}{\myemail} &
 \textit{GitHub:}     & \href{https://github.com/drpeteb}{drpeteb} \\
 \textit{LinkedIn:}   & \href{https://www.linkedin.com/in/drpetebunch/}{https://www.linkedin.com/in/drpetebunch/} & 
 \textit{Scholar:}    & \href{https://scholar.google.co.uk/citations?user=8q9tsLAAAAAJ}{Pete Bunch}
 %\textit{Skype:}      & \myskypenumber \\
\end{tabular}
\sepspace



% Statement
\NewPart{Summary and Skills}
Devising and applying statistical models to glean insights from data intrigues me. I have diverse experience solving statistical problems in varied domains, from ad targeting to retail forecasting to paleoclimatology. Along the way I have developed an enthusiasm for writing clean, modular and reusable software.

\Details{
\begin{itemize}
 \item Successful record as technical lead on projects focussing on inference and optimization.
 \item Broad knowledge of modern statistical modeling and machine learning theory and practice.
 \item Experience with distributed systems and map-reduce, primarily with Quantcast's proprietary Hadoop-like stack.
 \item Proficient with Java, Python (including NumPy, \href{https://github.com/scipy/scipy/pull/5296}{SciPy}, Pandas and Jupyter), MATLAB and various flavours of SQL. Familiarity with C, C++, and Scala.
\end{itemize}
}



% Work experience
\NewPart{Employment}

\WorkEntry{Modeling Scientist (Staff since March 2018, Senior since July 2016)}{2015 --- present}{Quantcast, Brand Advertising}{
\begin{itemize}
 \item Lead data scientist responsible for modeling, real time bidding and control systems fundamental to advertising campaigns targeting specific audience segments. Primarily technical contributions, but with a growing role in project leadership and wider engineering strategy.
 \item Masterminded the design and implementation of a new framework to target and trade off between multiple customer performance goals, including derivation of optimal pricing equations, development of a new control system, and planning and coordination of software changes across the bidding stack, resulting in reliable and consistent performance and fewer unhappy customers.
 \item Wrote new libraries for real-time model scoring, vastly reducing code complexity and adding a new layer of abstraction, facilitating faster product development, cleaner code deployment, and reducing both computational load and developer pain.
 \item Upgraded the statistical methodology underlying the A/B test framework, introducing Bayesian inference and hypothesis testing, and providing a rigorous foundation for assessing hundreds of modeling experiments.
 \item Improved log parsing algorithms to extract double the volume of label data for the flagship search product.
 \item Investigated numerous improvements to demographic modeling, including alternative multi-class classification models, methods for model calibration, and unsupervised approaches to discovering hidden classes.
 \item Won a company-wide hackathon for innovations in bid pricing strategies, and granted three trade secret awards.
 \item Mentored two summer interns and a winning intern hackathon team.% and gave regular ``Modeling Onboarding'' talks.
\end{itemize}
}
\sepspace

\WorkEntry{Data Scientist and Modeling Consultant}{2014 --- 2015}{Tesco, Supply Chain Development}{
\begin{itemize}
 \item Developed custom statistical models and learning algorithms for probabilistic forecasting, and implemented them with MATLAB and SQL to run at scale on a Teradata data warehouse.
 \item Reduced annual waste by \pounds12M.
\end{itemize}
}
\sepspace

\WorkEntry{Postdoctoral Research Associate}{2014 --- 2015}{Cambridge University Engineering Department}{
\begin{itemize}
 \item Devised a number of new Markov chain Monte Carlo algorithms for machine learning with dynamical systems.
 %\item Created a lab series of `Coffee Conference' internal seminars. Conducted undergraduates admissions interviews.
 \item Taught undergraduate engineers in MATLAB, signal processing, and mathematics. \\ (Modules included linear algebra, probability, vector calculus, differential equations, and filter design.)
\end{itemize}
}
\sepspace

%\WorkEntry{Summer Intern -- Paid}{Jun --- Aug 2009}{Metaswitch Networks, Network Protocols Division}{
%\begin{itemize}
%  \item Developed software in C and Python, adding support for a new protocol to client-deliverable product code, for a leading telecomms software company.
%\end{itemize}
%}
%\sepspace

%\WorkEntry{Industry Intern -- Paid, and DSTL Scholar}{2005 --- 2010}{DSTL (Defence Science \& Technology Laboratories), Electronics Department}{
%\begin{itemize}
%  \item Designed algorithms for in-service and prototype radio frequency detectors for military search applications.
%  \item Lead a \pounds300,000 program of research into acoustic landmine detection technology.
%\end{itemize}
%}



%% Skills
%\NewPart{Skills and Experience}




% Education
\NewPart{Education}

\MainHeading{University of Cambridge, Cambridge, UK}

\EducationEntry{PhD in Statistical Modeling and Algorithm Design}{2010 --- 2014}{
\begin{itemize}
 \item Thesis: \textit{``Particle filtering and smoothing algorithms for challenging time series models.''}
 \item Formulated and applied statistical models and Bayesian algorithms for inference and learning.
 \item Worked on theoretical and applied projects, including development of new sequential Monte Carlo methods, and algorithm design for detection of heartbeats in cardiography data.
\end{itemize}
}
\sepspace

\EducationEntry{BA \& MEng in Information Engineering (1$^{\text{st}}$ with Distinction)}{2006 --- 2010}{
\begin{itemize}
  \item Highest mark in the class in 2008 and 2010; second highest in 2009. Equivalent of 4.0 GPA every year.
  \item Modules in signal processing, communications, control, hardware and software architecture, and electronics.
\end{itemize}
}



\NewPart{Research}
\Details{
\begin{itemize}
 \item Main author on four journal and six conference papers on sequential and Markov chain Monte Carlo algorithms.
 \item Presented research at four international conferences, including oral and poster sessions.
 \item Co-author on two paleoclimatology papers, using Bayesian analysis with ice core data to infer the past state of the west Antarctic ice sheet.
\end{itemize}
}



% Fun Stuff
\NewPart{Activities}

\Details{
\begin{itemize}
 \item Avid beach runner, wannabe cyclist, pianist and  pine cone photographer
 \item Men's Captain, Cambridge '99s Rowing Club. Led team racing at Henley Royal Regatta. 2013 -- 2014
 \item Captain, Cambridge University Sailing Team. Semi-finals of University Nationals. 2007 -- 2008
\end{itemize}
}

\end{document} 